学術論文

### 2020-12-24 articles.Rmd
update

@@

>>>>

- [32] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(in press) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology,

@@

- [31] Kato, A., Kunisato, Y., Katahira, K., Okimura, T., & Yamashita, Y. (2020) Computational Psychiatry Research Map (CPSYMAP): a New Database for Visualizing Research Papers. Frontiers in Psychiatry, 11, 1360.[Link](https://www.frontiersin.org/articles/10.3389/fpsyt.2020.578706/full)
